---
title: "Tambola_Housie Game"
output: html_document
date: "2023-05-11"
runtime: shiny
---

```{r setup, include=FALSE}
if(! require("shinyWidgets")) {install.packages("shinyWidgets")} + library(shinyWidgets)
if(! require("shiny")) {install.packages("shiny")} + library(shiny)
if(! require("shinyMatrix")) {install.packages("shinyMatrix")} + library(shinyMatrix)
```

## Embedded Application User Interface

```{r tabsets, echo=FALSE}
ui <- fluidPage(
  setBackgroundImage(src = "https://www.shutterstock.com/image-photo/bingo-lotto-on-wooden-background-260nw-765127483.jpg", shinydashboard = FALSE),
  titlePanel("Housie Game"),
  sidebarLayout(
    sidebarPanel(
      h4("Number Called : "),
      h3(column(width = 6,verbatimTextOutput("Number"))),
      actionButton("generate", "Generate Number"),
      actionButton("reset", "Reset"),
      ),
    mainPanel(
      
      matrixInput("matrix", 
                  label = "Housie Matrix", 
                  value = matrix(rep(0, 100), nrow = 10, ncol = 10),
                  rows = list(names = FALSE),
                  cols = list(names = FALSE),
                  class = "numeric")
    )
  )
)

```

### Server

```{r}
server <- function(input, output, session) {
  
  rows<-10
  columns<-10
  
  called_numbers <- reactiveVal(vector("numeric"))
  
  generate_random_number <- function() {
    unique(sample(rep(1:90), 90, replace = F))
    
  }
  
  observeEvent(input$generate, {
    new_number <- generate_random_number()
    called_numbers(c(called_numbers(), new_number))
    
    
    
    matrix_data <- input$matrix
    first_zero <- which(matrix_data == 0)[1]
    if (!is.na(first_zero)) {
      matrix_data[first_zero] <- new_number
      updateMatrixInput(session, "matrix", value = matrix_data)
    }
    output$Number <- renderPrint({
      as.numeric(new_number[1])
    })
    
  })
  
  observeEvent(input$reset, {
    called_numbers(vector("numeric"))
    updateMatrixInput(session, "matrix", value = matrix(rep(0, rows * columns), nrow = rows, ncol = columns))
  })
  
}

shinyApp(ui, server,options = list(launch.browser =T))

```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.
